Software Citation Principles

### 2016-03-21 sc-principles/software-citation-principles.tex
adding UK to SSI

Some of the most actionable work has come from the Software Sustainability Institute (SSI) in the form of blog posts written by their community fellows:

>>>>

Some of the most actionable work has come from the UK Software Sustainability Institute (SSI) in the form of blog posts written by their community fellows:
